---
title: "Session 8: Remotes - Introduction"
date: 2024-12-06T10:15
format: revealjs
metadata-files:
  - _slides.yml
session-title: "Remotes - Introduction"
chapter: |
  ["Remotes: Introduction"](https://lennartwittkuhn.com/version-control-book/chapters/remotes-intro.html)
quiz-url: https://version-control-github.formr.org/
---

# Admin

## Schedule

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
create_schedule()
```

# Last session: Quarto Workshop

## Last session: Quarto Workshop

{{< fa display >}} [https://lennartwittkuhn.com/version-control-course-uhh-ss24/sessions/session06](https://lennartwittkuhn.com/version-control-course-uhh-ss24/sessions/session06)
```{=html}
<iframe width="100%" height="80%" src="https://lennartwittkuhn.com/version-control-course-uhh-ss24/sessions/session06" title="Version Control Book"></iframe>
```

## Last session: Questions about Quarto?

::: {.fragment}

### Cool, Quarto, but what now?

- We encourage you do use the `{{< var course.project >}}.qmd` from now on to develop your `{{< var course.project >}}` project!
  - You can move all content from `{{< var course.project >}}.txt` to `{{< var course.project >}}.qmd`.
  - Motivation: We can later turn your `{{< var course.project >}}` repository into a website (see [Lennart's example](https://lennartwittkuhn.com/uhh-eur-city-guide/))
- You can also just continue using the `{{< var course.project >}}.txt` file.
- **Reminder:** It's about implementing the Git exercises.
It does not matter if you use a `.qmd`, `.txt` or another file.

:::

# This session: {{< meta session-title >}}

## {{< meta session-title >}}

![Image from [Techdobz](https://medium.com/analytics-vidhya/version-control-using-git-github-ff4c3f7c752e)](../images/git-github-integration.png){width="70%"}

## Reading

{{< fa display >}} {{< meta chapter >}}

```{=html}
<iframe width="100%" height="80%" src="https://lennartwittkuhn.com/version-control-book/chapters/remotes-intro.html" title="Version Control Book"></iframe>
```

## Learning objectives

### {{< meta session-title >}}

{{< include ../objectives/_objectives-remotes-intro.qmd >}}

## Cheatsheet

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
knitr::kable(table_cheatsheet(name = "remote_intro"), format = "markdown", row.names = FALSE)
```

## Tasks

{{< include tasks-template.qmd >}}

## `{{< var course.project >}}` project

{{< include project/project-remotes-intro.qmd >}}

::: {.fragment}

### Today's team topic

- Interview each other about your favorite **place for a night out (dinner :shallow_pan_of_food:, drinks :tropical_drink: , dance :dancer:, concert :musical_note:**).
- Add the recommendation *of your partner* to your text file **or Quarto file**.
- Help each other in completing the exercises.

:::

## Exercises

### Connect to remote repositories using SSH

{{< include ../exercises/_exercises-remotes-ssh.qmd >}}

### Upload your local repository to a remote repository

{{< include ../exercises/_exercises-remotes-push.qmd >}}

## Bonus exercises

### :rocket: Optional: Add a `README.md`

{{< include ../exercises/_exercises-remotes-readme.qmd >}}

### :rocket: Optional: Clone and sync your repository

{{< include ../exercises/_exercises-remotes-clone.qmd >}}

## Solutions

### Connect to remote repositories using SSH

```{zsh, filename="Code"}
#| eval: false
#| file: exercises/code-exercises-remotes-ssh.sh
```
{{< include ../exercises/_solutions-remotes-ssh.qmd >}}

## Solutions

### Upload your local repository to a remote repository

```{zsh, filename="Code"}
#| eval: false
#| file: exercises/code-exercises-remotes-push.sh
```
{{< include ../exercises/_solutions-remotes-push.qmd >}}

## Solutions

### :rocket: Optional: Add a `README.md`

{{< include ../exercises/_solutions-remotes-readme.qmd >}}

## Solutions

### :rocket: Optional: Clone and sync your repository

```{zsh, filename="Code"}
#| eval: false
#| file: exercises/code-exercises-remotes-clone.sh
```
{{< include ../exercises/_solutions-remotes-clone.qmd >}}
