---
title: "Session 9: GitHub - Collaboration"
date: 2024-12-13T10:15
format: revealjs
metadata-files:
  - _slides.yml
session-title: "GitHub - Collaboration"
chapter: |
   ["GitHub - Advanced"](https://lennartwittkuhn.com/version-control-book/chapters/github-advanced.html)
quiz-url: https://version-control-github.formr.org
---

# Admin

## Schedule

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
create_schedule()
```

# Last session: GitHub - Intro

## Last session: GitHub - Intro

{{< fa display >}} [https://lennartwittkuhn.com/version-control-book/chapters/remotes-intro.html](https://lennartwittkuhn.com/version-control-book/chapters/remotes-intro.html)
```{=html}
<iframe width="100%" height="80%" src="https://lennartwittkuhn.com/version-control-book/chapters/remotes-intro.html" title="Version Control Book"></iframe>
```

## Last session's learning objectives

{{< include ../objectives/_objectives-remotes-intro.qmd >}}

## Questions about the last session?

# This session: {{< meta session-title >}}

## {{< meta session-title >}}

::: fragment
![Image from [Techdobz](https://medium.com/analytics-vidhya/version-control-using-git-github-ff4c3f7c752e)](../images/git-github-integration.png){width="70%"}
:::

## GitHub Flow

::: fragment
![Image from [Sebass van Boxel](https://github.com/SvanBoxel/release-based-workflow/issues/1)](../images/github_flow.png){width="70%"}
:::

## This and next session's learning objectives

{{< include ../objectives/_objectives-github-advanced.qmd >}}

## Reading

{{< fa display >}} {{< meta chapter >}}

```{=html}
<iframe width="100%" height="80%" src="https://lennartwittkuhn.com/version-control-book/chapters/github-advanced.html" title="Version Control Book"></iframe>
```

## Cheatsheet

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
knitr::kable(table_cheatsheet(name = "github_advanced"), format = "markdown", row.names = FALSE)
```

## Tasks

{{< include tasks-template.qmd >}}

## `{{< var course.project >}}` project

{{< include project/project-github-advanced.qmd >}}

::: {.fragment}

### Today's team topic

- Interview each other about your *least* favorite place or **place to avoid** (and, maybe, also why ...)
- Add the recommendation *of your partner* to your text file **or Quarto file**.
- Help each other in completing the exercises.

:::

## Exercises

### "Private" collaboration with pull requests (using GitHub Flow)

{{< include ../exercises/_exercises-remotes-collaboration.qmd >}}

::: fragment

### Add a `README.md`

{{< include ../exercises/_exercises-remotes-readme.qmd >}}

:::

## Bonus exercises

### :rocket: Optional: Clean up your repository

Files that your repository should include:

- a `{{< var course.project >}}.qmd` (see exercise in [Session 07](session07.qmd) on "Quarto") or `{{< var course.project >}}.txt` file (see exercises starting in [Session 02](session02.qmd)), or a similarly named file that includes the entries for the `{{< var course.project >}}` project
- a `.gitignore` file (see exercise in [Session 04](session04.qmd) on "Basic Git workflow")
- a `README.md` file (see exercise in [Session 09](session09.qmd) on "{{< meta session-title >}}")

While this is not mandatory, please try to remove any unnecessary files or clutter, like empty `.txt` files from your repository.
You can delete files directly on GitHub by clicking on the three dots next to the directory or file and selecting "Delete file," then commit the changes.
This effectively runs `git add` and `git commit` on GitHub.
Alternatively, delete them from your local repository, add, commit and push the changes to GitHub.
